\section{EXTRACURRICULAR}

\begin{minipage}[t]{0.45\linewidth} 
  \resumeSubHeadingListStart
    % CCLUB Supervisory Board
    \resumeSubheading
    {
      \href{https://cclub.metu.edu.tr/}{METU Computer Club \raisebox{-0.1\height}\faExternalLink} 
    }
    {07.2022 -- Present}
    {\underline{Supervisory Board}}
    {}
    \resumeItemListStart
      \resumeItem{\normalsize{Helping organizing $4^{th}$ \href{https://kodtu.cclub.metu.edu.tr/}{\textbf{KODTÜ}}, competitive programming contest among METU students, and $26^{th}$ \href{https://yarisma.cclub.metu.edu.tr/}{\textbf{Annual Programming Contest}}, one of the biggest competitive programming contests of Turkey, to help people to improve themselves in Computer Science.}}
      \resumeItem{\normalsize{Helping organizing \textbf{Informatics Day 2023}, an event that brings together the leading names of the informatics sector with people who are enthusiastic about informatics.}}
    \resumeItemListEnd

    % Research Group
    \resumeSubheading
    {Research Group}
    {03.2022 -- 06.2022}
    {}
    {}
    \resumeItemListStart
      \resumeItem{Studied with \href{https://user.ceng.metu.edu.tr/~karagoz/}{Prof. Dr. Pınar Karagöz}, one of the academicians in METU, in bachelor's degree research group.}
      \resumeItem{Data collections and classification of the data.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\end{minipage}
\hspace*{0.03\linewidth}
\begin{minipage}[t]{0.45\linewidth}
  \resumeSubHeadingListStart

    % CCLUB Board Member
    \resumeSubheading
    {
      \href{https://cclub.metu.edu.tr/}{METU Computer Club \raisebox{-0.1\height}\faExternalLink}
    }
    {08.2021 -- 07.2022}
    {\underline{Board Member}}
    {}
      \resumeItemListStart
        \resumeItem{\normalsize{Organized various events such as conferences and workshops.}}
        \resumeItem{\normalsize{Organized $3^{rd}$ \href{https://kodtu.cclub.metu.edu.tr/}{\textbf{KODTÜ}}, and $25^{th}$ \href{https://yarisma.cclub.metu.edu.tr/}{\textbf{Annual Programming Contest}} to help people to improve themselves in Computer Science.}}
        \resumeItem{\normalsize{Organized \href{https://kty.li/gfxI3}{\textbf{Informatics Day 2022}}}.}
      \resumeItemListEnd
        
    % CCLUB Member
    \resumeSubheading
    {
      \href{https://cclub.metu.edu.tr/}{METU Computer Club \raisebox{-0.1\height}\faExternalLink}
    }
    {09.2020 -- Present}
    {\underline{Active Member}}
    {}
      \resumeItemListStart
        \resumeItem{\normalsize{Helping organizing $24^{th}$ \href{https://yarisma.cclub.metu.edu.tr/}{\textbf{METU CClub Programming Contest}}, one of the biggest competitive programming contests of Turkey, to help people to improve themselves in Computer Science.}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\end{minipage}
