\section{PROJECTS}

\resumeSubHeadingListStart
  \resumeProjectHeading
  {
    {\textbf{\large{\underline{Book Portal}}}} 
    $\Big|$ 
    \large{\textit{Java / Spring - JavaScript / React}}
  }
  {08.2022}
    \resumeItemListStart
      \resumeItem{\normalsize{Developed in the internship at OBSS.}}
      \resumeItem{\normalsize{Has admin and user type log-in system. New users and books can be added to database. Adding, deleting and updating can be done on both users and books. Also, users can add books to their read and favorite lists.}}
      \resumeItem{\normalsize{Using Spring as the \resumeLink{https://github.com/burakmetehan/book-portal-backend}{back-end}, and React and Ant Design (React UI framework) as the \resumeLink{https://github.com/burakmetehan/book-portal-frontend}{front-end}.}}
    \resumeItemListEnd
  
    \vspace{-15pt}

  \resumeProjectHeading{
    \textbf{\large{\underline{Research Group}}}
  }{03.2022 -- 06.2022}
    \resumeItemListStart
      \resumeItem{Studied with \resumeLink{https://user.ceng.metu.edu.tr/~karagoz/}{Prof. Dr. Pınar Karagöz}, one of the academicians in METU, in the bachelor's degree research group.}
      \resumeItem{The study in which public opinion on Cappadocia is analyzed was about text mining. I focused on data collection with scrappers and organization of data using Python parser.}
    \resumeItemListEnd

  \vspace{-15pt}
  
  \resumeProjectHeading
  {
    \href
      {https://github.com/burakmetehan/Tracker}
      {\textbf{\large{\underline{Tracker}}} \raisebox{-0.1\height}\faExternalLink }
      $\Big|$
      \large{\textit{Python - Tkinter}}
  }
  {09.2021}
    \resumeItemListStart
      \resumeItem{\normalsize{Basic Todo tracker with GUI and basic features such as adding, completing and saving a task by its completion time by using the built-in timer.}}
      \resumeItem{\normalsize{Using OOP (Object Oriented Programming) and \resumeLink{https://docs.python.org/3/library/tkinter.html}{Tkinter} in Python.}}
      \resumeItemListEnd 
\resumeSubHeadingListEnd
